### 2021-07-22 doc/thesis/chapters/hls.tex
data types

This section gives a brief overview of the \cplusplus\ HLS code style that is supported with Xilinx tools.
More detailed information can be found in the respective user guide \cite{VivadoUgHLS}.

@@

>>>>

This section gives a brief overview of some HLS-specific \cplusplus\ features that are supported with Xilinx tools.
More detailed information can be found in the respective user guide \cite{VivadoUgHLS}.

@@

HLS supports special data types, which are not available in standard \cplusplus.
The focus of these data types is mainly to support an optimized translation into RTL, which requires the least amount of logic cells in the FPGA.\\

Standard \cplusplus\ only supports variables in the bitwidth of byte-boundaries, so in multiples of 8 bit.
However, this may be inefficient to fit into available FPGA hardware.
One example therefor is the DSP48 macro that Xilinx FPGAs have built-in.
They support the multiplication of only up to 18 bit.
In an example application, the reachable number range of a variable might be limited to 17 bit for the multiplication.
However, in order to represent that, using a 32 bit data type would be necessary in standard \cplusplus.
The HLS compiler does not have this prior knowledge of the number range limit and would thus implement a 32 bit multiplication, which is a waste of resources in this case.
Because of this reason, a major feature of HLS is the possibility to define data types with arbitrary bitwidths.
In that way, the above example can be optimized to use a data type that has a bitwidth of 17 bit, which is wide enough for the application.

todo: fixed point
